### 2016-06-23 paper/numerical_experiments.tex
small edit

The domain divisions for the three adaptive iterations are shown in Figure~\ref{fig:divvy3D}. We see that the error decomposition causes the first refinement iteration to target the QoI region and observations. %is there a way to see if any observations are more 'important' than others?
%
\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/divvy1_whitebg_shiftaxes.png} 
\caption{MF$_1$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/divvy2_whitebg_shiftaxes.png} 
\caption{MF$_2$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/divvy3_whitebg_shiftaxes.png} 
\caption{MF$_3$}
\end{subfigure}
\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
\label{fig:divvy3D}
\end{figure} 
%
The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations. We also compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose at each iteration the basis functions with the largest $5\%$ of the error for model refinement. Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations.
%
\begin{table}[h]
\centering
\begin{tabular}{c|c|c|c|c|c}
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
& & & (Estimated) & (Actual) & Time (s) \\ \hline
LF   & 0    &  &  & -0.48784 & 160 \\
MF01 &  &  &  &  &  \\
MF02 &  &  &  &  &  \\
MF03 &  &  &  &  &  \\
MF04 &  &  &  &  &  \\
MF05 &  &  &  &  &  \\
MF06 &  &  &  &  &  \\
HF   & 100  & 547420  & 0        & 0        & 6210 \\
\end{tabular}
\caption{Runtime and relative errors of adaptive algorithm iterations.}
\label{tab:ref3D}
\end{table}
%
%similar final refinement percentage
%can we get a better sense of 'important' observations?
%same weird sign flip at end
%actual relative error decreases monotonically in magnitude, but not estimated...

>>>>

The domain divisions for the three adaptive iterations are shown in Figure~\ref{fig:divvy3D}. We see that the error decomposition causes the first refinement iteration to target the QoI region and observations. %is there a way to see if any observations are more 'important' than others?
%
\begin{figure}[h]
\centering
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/divvy1_whitebg_shiftaxes.png} 
\caption{MF$_1$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/divvy2_whitebg_shiftaxes.png} 
\caption{MF$_2$}
\end{subfigure}
\begin{subfigure}[t]{0.32\textwidth}
\centering
\includegraphics[width=\textwidth]{series3D/divvy3_whitebg_shiftaxes.png} 
\caption{MF$_3$}
\end{subfigure}
\caption{Domain division for mixed-fidelity models (low-fidelity convection-diffusion model used in pink portion, high-fidelity convection-diffusion-reaction model used in blue portion).}
\label{fig:divvy3D}
\end{figure} 
%
The amount of time required by the adaptive algorithm of course depends on the chosen error tolerance as well as the amount of additional model refinement between successive iterations. We also compare the runtimes for a more conservative choice of refinement rate; given the same error tolerance, we instead choose at each iteration the basis functions with the largest $5\%$ of the error for model refinement. Table~\ref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations.
%
\begin{table}[h]
\centering
\begin{tabular}{c|c|c|c|c|c}
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & Total \\ 
& & & (Estimated) & (Actual) & Time (s) \\ \hline
LF   & 0    & 1068856 & -0.37511 & -0.48784 & 160 \\
MF01 & 9.27 & 613419  &  &  &  \\
MF02 & 16.9 & 558523  &  &  &  \\
MF03 & 23.7 & 550323  &  &  &  \\
MF04 & 30.4 & 548225  &  &  &  \\
MF05 & 37.2 & 547744  &  &  &  \\
MF06 & 44.6 & 547532  &  &  &  \\
HF   & 100  & 547420  & 0        & 0        & 6210 \\
\end{tabular}
\caption{Runtime and relative errors of adaptive algorithm iterations.}
\label{tab:ref3D_dainty}
\end{table}
%
%similar final refinement percentage
%can we get a better sense of 'important' observations?
%same weird sign flip at end
%actual relative error decreases monotonically in magnitude, but not estimated...
